### 2018-10-10 post-linearity-2018/LAM.tex
Some small changes.

Finally, we proved strong normalization of CNC logic via a translation to
LNL logic. The proof is in Appendix~\ref{app:strong-normalization}. We first
define a function $CL$ that maps our term assignment for natural deduction
to Benton's term assignment, and then shows that if there is reduction
$[[t1 ~> t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
$CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in LNL. Recall
that a LNL model consists of an adjunction $F:\cat{C}\dashv\cat{L}:G$ in
which $\cat{C}$ is a cartesian closed category and $\cat{L}$ is a SMCC.
The basic idea of mapping a LAM model to a LNL model is mapping the SMCC in
LAM to the cartesian closed category in LNL, and the Lambek category in LAM
to the SMCC in LNL. For instance, $s_1\triangleright s_2$ in CNC, where
$[[s1]]$ and $[[s2]]$ are atomic terms, maps to $s_1\otimes s_2$ in LNL.

>>>>

\noindent
Finally, we have strong normalization of CNC logic.

\begin{theorem}[Strong Normalization]
  \label{thm:strong-normalization}
  CNC logic is strongly normalizing.
\end{theorem}
\begin{proof}
  The proof is via a translation to LNL logic. The proof is in
  Appendix~\ref{app:strong-normalization}. We first define a function
  $CL$ that maps our term assignment for natural deduction to Benton's
  term assignment, and then shows that if there is reduction $[[t1 ~>  t2]]$ (resp. $[[s1 ~> s2]]$) in CNC, then there is a reduction
  $CL(t_1)\leadsto CL(t_2)$ (resp. $CL(s_1)\leadsto CL(s_2)$) in
  LNL. Recall that a LNL model consists of an adjunction
  $F:\cat{C}\dashv\cat{L}:G$ in which $\cat{C}$ is a cartesian closed
  category and $\cat{L}$ is a SMCC.  The basic idea of mapping a LAM
  model to a LNL model is mapping the SMCC in LAM to the cartesian
  closed category in LNL, and the Lambek category in LAM to the SMCC in
  LNL. For instance, $s_1\triangleright s_2$ in CNC, where $[[s1]]$ and
  $[[s2]]$ are atomic terms, maps to $CL(s_1)\otimes CL(s_2)$ in LNL.
\end{proof}
